---
title: "Ego centric network for Academic motivation"
author: ""
date: "`r Sys.Date()`"
output: html_document
---


```{r include=FALSE} 
library(igraph)
library(tidyverse)
library(dplyr)
library(egor)
library(ggraph)
library(intergraph)
library(tidygraph)
library(statnet)
library(Hmisc)
library(reticulate)
library(knitr)
library(rmarkdown)
```

### Data cleaning
```{r}
egoattributes <- read.csv("SNAP-19-SN_March+13,+2025_09.45.csv")
##Remove those with empty egoties
egoattributes[770:775, 50:51] #detect where is the old/new data boundary
alldat<- egoattributes %>%
  filter(row_number() >= 773)
alldat[1:5, 50:51] #confirm the cutoff is correct

alldat<- subset(alldat, DistributionChannel!="preview") #remove non-data (preview only)
nrow(alldat)

##assign ID numbers
alldat$egoID <- 1001:(1000+nrow(alldat))

```

## Initital Sample

```{r}
originaln<-nrow(alldat) # 1732 (total signed up for the study)
## Cleaning by "Finished" rate
alldat <- subset(alldat, Finished==1) 
##Cleaning by participants' incomplete data not detected by "finished"
alldat <- subset(alldat, egoID!=1047)
alldat <- subset(alldat, egoID!=1184)
##Cleaning by participants who did not answer any alters and thus considered incomplete
alldat<- subset(alldat, nchar(Q1_1)!=0) 
incompleten<-nrow(alldat) # 1486 (after cleaning all incomplete)

alldat <- subset(alldat, egoID!="1553") #random answers
randomn<-nrow(alldat) #1485

## Cleaning by participants who answered less than 5 minutes
##Other cleaning
alldat<- subset(alldat, Duration..in.seconds.>=300) 
shortn<-nrow(alldat) # 1052

#Hmisc::describe(alldat$Q119)
```


### clean inappropriate alter names

Check:
```{r}
#unique(alldat$Q19_7_TEXT)
```


```{r}

#same ip, time, names
#alldat <- filter(alldat, !(Q1_1 %in% c("yvonne meaux", "Yvonne meaux")))

#alldat[alldat$egoID==1815, ]
##1762??? i m her grandchild not 
##2000???
#1271 god
alldat$Q19_7_TEXT[alldat$Q22_3_TEXT=="He's God"]<-"god"
##1818/1819

#columns 19-28 = alternames
for (i in 19:28){
  alldat[,i]<-tolower(alldat[,i])
  alldat[,i][alldat[,i]=='na' & alldat$Q43 == 3] <- "incorrect"
  alldat[,i][alldat[,i]=='n.a'|alldat[,i]=='n/a'|alldat[,i]=='na'|alldat[,i]=='-'|alldat[,i]=='--'|alldat[,i]==' '] <- "incorrect"
  alldat[,i][alldat[,i]=='myself'] <- "incorrect"
  alldat[,i][grepl('god',alldat[,i])] <- "incorrect"
##Cleaning by participants who answered any incorrect alters
  alldat<-subset(alldat, alldat[,i]!="incorrect")
}
```


### clean inappropriate alter relationships (myself/God)

```{r}
#identify columns number
alterrelat_var<-c(30,41,53,66, 80, 95,111,128,146,165)

###code all inappropriate relation with 999 so that later when deleting ties, we can use 999 to identify and delete inappropriate ties (rather than deleting the data of the whole participant)

for (i in alterrelat_var){
  alldat[,i]<-tolower(alldat[,i])
  alldat[,i-1][alldat[,i] %in% c('myself','myself ','self','me', 'he is god.','god', 'dog', 
                                 "it's me ;)")] <- 999 #"bad person" seem legit and was not deleted. 
  alldat[,i-1][grepl('self|god|myself|me', alldat[,i])]<-999
  alldat[,i][alldat[,i] %in% c('myself','myself ','self','me', 'he is god.','god', 'dog', #recode relationship as NA
                                 "it's me ;)")] <- "incorrect"
##Cleaning by participants who answered any inappropriate alters
  alldat<-subset(alldat, alldat[,i-1]!=999)
  alldat<-subset(alldat, alldat[,i]!="incorrect")

}
namen<-nrow(alldat) #after cleaning god/myself 968

###alldat[,i][startsWith(alldat[,i], "it")]<-''

```

### Code alter relationships

1 = Parent
2 = Child (recode to combine with 1)
3 = Sibling
4 = Relative
5 = Spouse/romantic partner/sig other
6 = Friend/peer
7 = Other (unidentified)
8 = teacher figures
9 = mental health professions (counselor, therapist, psychiatrist)
10 = other adults (caretaker role, nanny, parent figure)
11 = work
12 = church/religious

```{r}

for (i in alterrelat_var){
  alldat[,i]<-tolower(alldat[,i])

  alldat[,i-1][alldat[,i-1]==2]<-1 #all parent-child categories, including step

  alldat[,i-1][grepl('pastor|church|minister',alldat[,i])] <- 12  #church
  alldat[,i][grepl('pastor|church|minister',alldat[,i])] <- "church"  #church

  alldat[,i-1][grepl("friends dad|family friend|boyfriends mom|mothers friend|bestfriends mom|friend's mom|doctor|chiropractor|owner of my house|patient|neighbor|sponsor|book|parentfig|my nanny|nfl player", alldat[,i])] <- 10
  alldat[,i][grepl("friends dad|family friend|boyfriends mom|mothers friend|bestfriends mom|friend's mom|doctor|chiropractor|owner of my house|patient|neighbor|sponsor|book|parentfig|my nanny|nfl player", alldat[,i])]  <- "othr_adults"

  alldat[,i-1][grepl('grand|gm|grandparent|grandchild', alldat[,i])] <-4
  alldat[,i][grepl('grand|gm|grandparent|grandchild', alldat[,i])] <-"grandparent"

  alldat[,i-1][alldat[,i] %in% c('cousin','uncle','uncle ','bnl'
                                 ,'aunt','brothers wife','brother in law','mother n law',
                                 'significant others parent','family','sister in law','brother-in-law',
                                 'sister  in law','sister-in-law')] <- 4 #relatives
  alldat[,i][alldat[,i] %in% c('cousin','uncle', 'uncle ', 'bnl'
                                 ,'aunt','brothers wife','brother in law','mother n law',
                                 'significant others parent','family','sister in law','brother-in-law',
                               'sister  in law','sister-in-law')] <- "relatives" #relatives
  
  alldat[,i-1][grepl('step|parent|mom|dad|mother|father|pa pa|moms bf|dads gf|legal guardian|pa pa', alldat[,i])] <- 1
  alldat[,i][grepl('step|parent|mom|dad|mother|father|pa pa|moms bf|dads gf|legal guardian|pa pa', alldat[,i])] <- "parentfig"

  alldat[,i-1][grepl('boss|work|employ',alldat[,i])] <- 11  #work exboss
  alldat[,i][grepl('boss|work|employ',alldat[,i])] <- "work"  #work
  
  alldat[,i-1][grepl('ex|former partner',alldat[,i])] <- 5 ##past/current sign other
  alldat[,i][grepl('ex|former partner',alldat[,i])] <- "sigother" #past/current sign other

  alldat[,i-1][grepl('classmate|organization leader|acquintance|friend|room|peer',alldat[,i])] <- 6 ##peer
  alldat[,i][grepl('classmate|organization leader|acquintance|friend|room|peer',alldat[,i])] <- "peer" #peer
  
  alldat[,i-1][grepl('couns|admin|mentor|student|band|college|teach|advis|tutor|councelor|chemistry aid|
                      academic|princ|school|train|coach|faculty|instructor|profess|guidance|educator',alldat[,i])] <- 8 #teacherfigures
  alldat[,i][grepl('couns|admin|mentor|student|band|college|teach|advis|tutor|councelor|chemistry aid|
                    academic|princ|school|train|coach|faculty|instructor|profess|guidance|educator',alldat[,i])] <- "academic" #MHfigures
  alldat[,i-1][grepl('therapist|psychiat',alldat[,i])] <- 9
  alldat[,i][grepl('therapist|psychiat',alldat[,i])] <- "mentalhealth"
  
  alldat[,i-1][alldat[,i] %in% c('dont know him','nothing','na','bad person ')] <- 7 #unidentified
  alldat[,i][alldat[,i] %in% c('dont know him','nothing','na','bad person ')] <- NA #unidentified

  #alldat[,i][alldat[,i]==""]<-NA
}

```
Check again
```{r}
# Combine all the data into one vector
combined_data <- c(alldat$Q2_7_TEXT, alldat$Q11_7_TEXT, alldat$Q19_7_TEXT, alldat$Q27_7_TEXT,
                   alldat$Q35_7_TEXT, alldat$Q43_7_TEXT, alldat$Q51_7_TEXT, alldat$Q59_7_TEXT,
                   alldat$Q67_7_TEXT, alldat$Q75_7_TEXT)

# Find unique values
unique_values <- unique(combined_data)

# Calculate the frequency of each unique value
frequency_table <- table(combined_data)

# Print the frequency table
print(frequency_table)

```

### Ego Attribute Dataset

```{r}

egoattributes <-  dplyr::select(alldat, egoID, Q94_1:Q120, -Q2_3_TEXT, -Q3_9_TEXT, - Q3_7_TEXT)
# Convert character columns with numeric values to numeric
egoattributes <- egoattributes %>%
  mutate_if(is.character, as.numeric)
str(egoattributes)
```

#### Recoding and finding reliability for ext_/external regulation 

```{r}

ext_reg <- select(egoattributes, Q94_1, Q96_2, Q98_3, Q100_4)
egoattributes$ext_reg<-rowMeans(ext_reg)
psych::alpha(ext_reg)$total$raw_alpha 
#describe(egoattributes$ext_reg)

```

#### Recoding and finding reliability for Intrinsic/to know
```{r}
int_toknow <- select(egoattributes, Q94_2, Q96_3, Q98_4, Q100_5)
egoattributes$int_toknow<-rowMeans(int_toknow)
#psych::alpha(int_toknow)
#describe(egoattributes$int_toknow)
```
***
#### Recoding and finding reliability for ext_/identified
```{r}
ext_iden <- select(egoattributes, Q94_3, Q96_4, Q98_5, Q100_6)
egoattributes$ext_iden<-rowMeans(ext_iden)
#psych::alpha(ext_iden)
#describe(egoattributes$ext_iden)
```
***

#### Recoding and finding reliability for Intrinsic/stimulation
```{r}
int_stim <- select(egoattributes, Q94_4, Q96_5, Q98_6, Q102_1)
egoattributes$int_stim<-rowMeans(int_stim)
#psych::alpha(int_stim)
#describe(egoattributes$int_stim)
```

***
#### Recoding and finding reliability for Amotivation
```{r}
amotiv <- select(egoattributes, Q94_5, Q96_6, Q100_1, Q102_2)
egoattributes$amotiv<-rowMeans(amotiv)
#psych::alpha(amotiv)
#describe(egoattributes$amotiv)
```

***
#### Recoding and finding reliability for Intrinsic/Accomplishment
```{r}
int_accomp <- select(egoattributes, Q94_6, Q98_1, Q100_2, Q102_3)
egoattributes$int_accomp<-rowMeans(int_accomp)
#psych::alpha(int_accomp)
#describe(egoattributes$int_accomp)
```

***
#### Recoding and finding reliability for ext_/introjected
```{r}
ext_intro <- select(egoattributes, Q96_1, Q98_2, Q100_3, Q102_4)
egoattributes$ext_intro<-rowMeans(ext_intro)
#psych::alpha(ext_intro)
#describe(egoattributes$ext_intro)
```

```{r}

egoattributes <- rename(egoattributes, ego.gender=Q2.1, ego.race=Q3, ego.workhours=Q4
                        , ego.studentorg=Q6.1, ego.belong=Q107
                        , ego.acadval=Q91_1, ego.careerval=Q92_1
                        , ego.age=Q119, ego.year=Q120
                        )

##Recode attritbues where necessary

egoattributes$ego.genderbi[egoattributes$ego.gender==1]<-0 #"female"
egoattributes$ego.genderbi[egoattributes$ego.gender==2]<-1 #"male"
egoattributes$ego.genderbi[egoattributes$ego.gender==3]<-NA #"non-binary"
egoattributes$ego.racetri[egoattributes$ego.race==1]<-1 #White
egoattributes$ego.racetri[egoattributes$ego.race==2]<-2 #Black
egoattributes$ego.racetri[egoattributes$ego.race>=3]<-3 #Other

```



## Alter Attributes with ego-alter ties

```{r}
##alter data by sequence
alter01<-dplyr::select(alldat, egoID, Q1_1, Q2:Q10_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter02<-dplyr::select(alldat, egoID, Q1_2, Q11:Q18_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter03<-dplyr::select(alldat, egoID, Q1_3, Q19:Q26_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter04<-dplyr::select(alldat, egoID, Q1_4, Q27:Q34_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter05<-dplyr::select(alldat, egoID, Q1_5, Q35:Q42_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter06<-dplyr::select(alldat, egoID, Q1_6, Q43:Q50_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter07<-dplyr::select(alldat, egoID, Q1_7, Q51:Q58_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter08<-dplyr::select(alldat, egoID, Q1_8, Q59:Q66_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)
alter09<-dplyr::select(alldat, egoID, Q1_9, Q67:Q74_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)

alter10<-dplyr::select(alldat, egoID, Q1_10, Q75:Q82_10_TEXT,
                           person21_1,  
                           Q110_4,  Q110_5,  
                           Q111_4,  Q111_5,  Q111_6, 
                           Q112_4,  Q112_5,  Q112_6,  Q112_7,  
                           Q113_4,  Q113_5,  Q113_6,  Q113_7,  Q113_8, 
                           Q114_4,  Q114_5,  Q114_6,  Q114_7,  Q114_8,  Q114_9,  
                           Q115_4,  Q115_5,  Q115_6,  Q115_7,  Q115_8,  Q115_9,  Q115_10,  
                           Q116_4,  Q116_5,  Q116_6,  Q116_7,  Q116_8,  Q116_9,  Q116_10,  Q116_11,  
                           Q117_4,  Q117_5,  Q117_6,  Q117_7,  Q117_8,  Q117_9,  Q117_10,  Q117_11,  Q117_12)

ChangeNames <- function(x) {
    names(x) <- c("egoID", "alter.initial", "egoalt_relation", "egoalt_relate_othr"
                     , "egoalter_tie", "egoalter_commfreq", "alter.gender"
                     , "alt.gender_othr"
                     , "alter.age", "alter.acad.val", "alter.career.val","alter.edu"
                     , "alter.edu.othr"
                  , "e0102"
                  , "e0103", "e0203"
                  , "e0104", "e0204", "e0304"
                  , "e0105", "e0205", "e0305", "e0405"
                  , "e0106", "e0206", "e0306", "e0406", "e0506"
                  , "e0107", "e0207", "e0307", "e0407", "e0507", "e0607"
                  , "e0108", "e0208", "e0308", "e0408", "e0508", "e0608", "e0708"
                  , "e0109", "e0209", "e0309", "e0409", "e0509", "e0609", "e0709", "e0809"
                  , "e0110", "e0210", "e0310", "e0410", "e0510", "e0610", "e0710", "e0810", "e0910")
    return(x)
}

ego.alt <- function(x, alterseq) {
  x<-ChangeNames(x)
  x$alterID <- alterseq
  x$alterID<-paste(x$egoID, x$alterID, sep="")
  #x<-subset(x, alter.initial!="")
  return(x)
}

alter01 <- ego.alt(alter01, "01") 
alter02 <- ego.alt(alter02, "02") 
alter03 <- ego.alt(alter03, "03") 
alter04 <- ego.alt(alter04, "04") 
alter05 <- ego.alt(alter05, "05") 
alter06 <- ego.alt(alter06, "06") 
alter07 <- ego.alt(alter07, "07") 
alter08 <- ego.alt(alter08, "08") 
alter09 <- ego.alt(alter09, "09") 
alter10 <- ego.alt(alter10, "10") 

alterlist <- mget(ls(pattern= "^alter.\\d$"))
alterattr <- alterlist %>% 
  reduce(full_join)


```

## alter characteristics at alter level 

```{r}
#alter_cleaned<-subset(alterattr, nchar(alter.initial)!=0)
alterattr$egoalter_tie<-as.numeric(alterattr$egoalter_tie)
alterattr$alter.age<-as.numeric(alterattr$alter.age)
alterattr$egoalter_commfreq<-as.numeric(alterattr$egoalter_commfreq)
alterattr$alter.career.val<-as.numeric(alterattr$alter.career.val)
alterattr$alter.edu<-as.numeric(alterattr$alter.edu)
alterattr$alter.acad.val<-as.numeric(alterattr$alter.acad.val)


Hmisc::describe(alterattr$alter.gender)

alterattr$alter.genderbi[alterattr$alter.gender==1]<-0 #female
alterattr$alter.genderbi[alterattr$alter.gender==2]<-1 #male
alterattr$alter.genderbi[alterattr$alter.gender==3]<-NA #non-binary

#summary(as.factor(alterattr$alter.edu))

```

## alter characteristics at ego level (summarise)
```{r}

ego_avgaltattr <- 
  alterattr %>%
  group_by(egoID) %>%
  summarise(mean.clo=mean(egoalter_tie, na.rm=T),
            mean.comm=mean(egoalter_commfreq, na.rm=TRUE),
            mean.careerval=mean(alter.career.val, na.rm=T), mean.acadval= mean(alter.acad.val, na.rm=TRUE),
            mean.edu = mean(alter.edu, na.rm=T), alt.edudiverse = n_distinct(alter.edu, na.rm=T),
            alt.type=n_distinct(egoalt_relation, na.rm=TRUE), alt.age=mean(alter.age, na.rm=T), alt.agesd=sd(alter.age,na.rm=T),
            alt.female= sum(alter.gender==2), alt.male= sum(alter.gender==1),
            alt.genratio = alt.female/alt.male)

egoattributes<-merge(egoattributes, ego_avgaltattr, by="egoID")

#update files
#write.csv(alterattr, "alter_attribute.csv")
#write.csv(egoattributes, "ego_attribute.csv")

```



## alter-alter relationships data

```{r}

ChangeNames2 <- function(x) {
    names(x) <- c("egoID", "from.alter", "alt.alt.tie","egoalt_relation", "egoalt_relate_othr", "alter.initial", "to.alter")
    return(x)
}


egoalter <-  dplyr::select(alterattr, egoID, alterID, alter.initial, egoalt_relation, egoalt_relate_othr
                          # Q1_1,  Q1_2,  Q1_3,  Q1_4,  Q1_5,  Q1_6,  Q1_7,  Q1_8,
                          # Q1_9,  Q1_10  #initials
                  , e0102
                  , e0103, e0203
                  , e0104, e0204, e0304
                  , e0105, e0205, e0305, e0405
                  , e0106, e0206, e0306, e0406, e0506
                  , e0107, e0207, e0307, e0407, e0507, e0607
                  , e0108, e0208, e0308, e0408, e0508, e0608, e0708
                  , e0109, e0209, e0309, e0409, e0509, e0609, e0709, e0809
                  , e0110, e0210, e0310, e0410, e0510, e0610, e0710, e0810, e0910)



y<-data.frame()
for (i in 1:10){
  for (j in (i+1):10){
    if (i<9 && j < 10){
      a=(paste("0",i,sep=""))
      b=(paste("0",j,sep=""))
      tmp<-subset(egoalter, endsWith(alterID, paste0("0",i)))
      tmp<-dplyr::select(tmp, egoID, alterID, ends_with(paste0(a,b)),egoalt_relation,egoalt_relate_othr,alter.initial)
      tmp$to.alter <- paste0(tmp$egoID, b) 
      tmp <- ChangeNames2(tmp)
      y<-rbind(y, tmp)
    }
    if (i<9 && j == 10){
      a=(paste("0",i,sep=""))
      b=(paste(j,sep=""))
      tmp<-subset(egoalter, endsWith(alterID, paste0("0",i)))
      tmp<-dplyr::select(tmp, egoID, alterID, ends_with(paste0(a,b)),egoalt_relation,egoalt_relate_othr,alter.initial)
      tmp$to.alter <- paste0(tmp$egoID, b) 
      tmp <- ChangeNames2(tmp)
      y<-rbind(y, tmp)
    }    
    if (i==9 ){
      a=(paste("0",i,sep=""))
      b=(paste(j,sep=""))
      tmp<-subset(egoalter, endsWith(alterID, paste0("0",i)))
      tmp<-dplyr::select(tmp, egoID, alterID, ends_with(paste0(a,b)),egoalt_relation,egoalt_relate_othr,alter.initial )
      tmp$to.alter <- paste0(tmp$egoID, b) 
      tmp <- ChangeNames2(tmp)
      y<-rbind(y, tmp)
    }
  }}

alter_ties = y
#write.csv(y, "alter_ties.csv")

```

## Clean alter ties that have no relationships 

Some alters do not know each other (relationship = 0) or have negative relationship (relationship weight<0). The origin weight variable is recoded so that 
- negative values of weight_origin = no relationship
- positive values = weight of 1

```{r}

#check responses
#unique(alter_tiestmp$egoalt_relate_othr)
#table(alter_tiestmp$egoalt_relate_othr)

#unique(alter_tiestmp$egoalt_relation)

#https://bookdown.org/rdpeng/rprogdatascience/regular-expressions.html

#regrex in r 
alter_tiestmp2 <- subset(alter_ties, nchar(alter.initial)!=0)

#alterattrtmp <- alterattr[((alterattr$alterID %in% alter_ties$from.alter)|(alterattr$alterID %in% alter_ties$to.alter)), ]  

alter_tiestmp2$alt.alt.tie<-as.numeric(alter_tiestmp2$alt.alt.tie)
#alter_tiestmp3<-subset(alter_tiestmp2, alt.alt.tie!="")


alter_tiestmp3<- dplyr::select(alter_tiestmp2, egoID, from.alter, to.alter, alt.alt.tie)
alter_tiestmp3<- rename(alter_tiestmp3, weight_origin=alt.alt.tie)
#alter_tiestmp3$weight<-alter_tiestmp3$weight_origin+10
alter_tiestmp3$weight<-alter_tiestmp3$weight_origin


alter_tiestmp3$weight[alter_tiestmp3$weight_origin<=0]<-NA #negative or no relationship
#alter_tiestmp3<-subset(alter_tiestmp3, is.na(alter_tiestmp3$weight)!=T)
#alter_tiestmp3$weight<-alter_tiestmp3$weight
describe(alter_tiestmp3$weight)
table(alter_tiestmp3$weight)
#write.csv(alter_tiestmp2,"alter_tiestmp2_allegos.csv")
#write.csv(alter_tiestmp3,"alter_tiestmp3.csv") #only with at least one alt-alt tie.
```

### egoIDs who completed the survey but did not report any alter-alter ties.
```{r}
# Get unique egoIDs from both datasets
egoIDs_in_tiestmp2 <- unique(alter_tiestmp2$egoID)
egoIDs_in_tiestmp3 <- unique(alter_tiestmp3$egoID)

# Identify egoIDs present in alter_tiestmp2 but not in alter_tiestmp3
missing_egoIDs <- setdiff(egoIDs_in_tiestmp2, egoIDs_in_tiestmp3)

# Print the missing egoIDs
print(missing_egoIDs)
finaln<-length(missing_egoIDs)
```

## Clean missing in all three sets

### screen excluded egos and alters
#and report final sample size after cleaning

```{r}


listtemp1<-unique(alter_tiestmp3$egoID) #number of screened participants
alters_screened<-c(alter_tiestmp3$from.alter, alter_tiestmp3$to.alter)
listtemp2<-unique(alters_screened) #number of alters
#number of alter-alter tie = alter_tiestmp3
#egoattributes<-read.csv("ego_attribute.csv")
egoattributes_tmp <- subset(egoattributes, (egoID %in% listtemp1))
#alterattr<-read.csv("alter_attribute.csv")
#alterattr$egoalter_tie_deci<-alterattr$egoalter_tie
#alterattr$egoalter_tie_deci[alterattr$egoalter_tie_deci<=0]<- NA
alterattr_tmp<-alterattr[complete.cases(alterattr),]
alterattr_tmp<-subset(alterattr_tmp, egoID %in% listtemp1)
alterattr_tmp<-subset(alterattr, alterID %in% listtemp2)
#alterattr_tmp$egoalter_tie_deci<-(alterattr_tmp$egoalter_tie_deci)/10
#$alter_tiestmp3<-subset(alter_tiestmp3, alterID %in% listtemp3)

describe(alterattr_tmp$egoalter_tie)
summary(as.factor(alterattr_tmp$egoalter_tie))

```

### descriptive statistics

```{r}
describe(egoattributes_tmp$ego.gender)
describe(egoattributes_tmp$ego.race)
egoattributes_tmp$ego.ager<-egoattributes_tmp$ego.age + 14
describe(egoattributes_tmp$ego.ager)
sd(egoattributes_tmp$ego.ager, na.rm=T)
describe(egoattributes_tmp$ego.year)
```


### Egor object generation

```{r}

egor.obj<-egor::threefiles_to_egor(egos= egoattributes_tmp, 
                                   alters.df = alterattr_tmp,
                                   edges = alter_tiestmp3,
                                   ID.vars=list(ego="egoID",
                                                alter="alterID",
                                                source="from.alter",
                                                target="to.alter")
                                   )

summary(egor.obj)

```

## Plot graphs for egos and find their network indices

```{r}

#https://r-graph-gallery.com/248-igraph-plotting-parameters.html

gr.list <- egor::as_igraph(egor.obj) #without ego
gr.list.ego <- egor::as_igraph(egor.obj, include.ego = TRUE) #with ego
#egor::as.egor(gr.list)

#gr<-gr.list[["2059"]]
#plot(gr)
#igraph::degree(gr)
#igraph::betweenness(gr) 
#igraph::edge_density(gr)
#igraph::centr_degree(gr)
#(igraph::eigen_centrality(gr)$vector)

#egor_vis_app(egor.obj) #shiny app

```

## Network indices (Descriptive analysis)

```{r}

centralitydf<- gr.list %>% 
  map_dfr(~tibble(
    mean.eigen=mean(igraph::eigen_centrality(.x)$vector),
    dens=edge_density(.x),
    mean.deg=mean(igraph::degree(.x)),
    mean.bet=mean(igraph::betweenness(.x)),
    deg.centr=centr_degree(.x)$centralization),
    .id="egoID")

egoattributes_tmp2<-merge(egoattributes_tmp, centralitydf, by ="egoID")
egoattributes_tmp<-merge(egoattributes_tmp, centralitydf, by ="egoID")
```



### Analyses using igraph

```{r}

alter.aca.value<- alterattr_tmp %>%
  group_by(egoID) %>%
  summarise_at(vars(alter.acad.val), list(alter.aca.value.avg=mean))

egoattributes_tmp<-merge(egoattributes_tmp, alter.aca.value, by ="egoID")
alter.career.value<- alterattr_tmp %>%
  group_by(egoID) %>%
  summarise_at(vars(alter.career.val), list(alter.career.value.avg=mean))

egoattributes_tmp<-merge(egoattributes_tmp, alter.career.value, by ="egoID")

cor.test(egoattributes_tmp$alter.aca.value.avg, egoattributes_tmp$ego.acadval)
cor.test(egoattributes_tmp$alter.career.value.avg, egoattributes_tmp$ego.careerval)

```


### Ego attributes correlation with network indices 

```{r}

egodense<-ego_density(egor.obj)
egodense<-rename(egodense, egoID=.egoID)
egoattributes_tmp <- merge(egoattributes_tmp, egodense, by="egoID")
describe(egoattributes_tmp$density)
sd(egoattributes_tmp$density)
```

### ego-alter homophily

```{r}

gendersim<-comp_ei(egor.obj, "alter.gender", "ego.gender")
gendersim<-rename(gendersim, egoID=.egoID, gendersim=ei)
egoattributes_tmp<-merge(egoattributes_tmp, gendersim, by ="egoID")

describe(egoattributes_tmp$gendersim)
sd(egoattributes_tmp$gendersim, na.rm=T)

```



#gender and age diversity
```{r}

composition(egor.obj,"alter.gender") #alter attribute only

alts_diversity_count(egor.obj, "alter.gender")
agediver <- alts_diversity_entropy(egor.obj, "alter.age")
agediver <- rename(agediver, egoID=.egoID, agediver=entropy)
egoattributes_tmp<-merge(egoattributes_tmp, agediver, by="egoID")

```

### h v. low belonging

```{r}
egoattributes_tmp$belong_cat<-NA
egoattributes_tmp$belong_cat[egoattributes_tmp$ego.belong>3]<-1
egoattributes_tmp$belong_cat[egoattributes_tmp$ego.belong<=3]<-0
egoattributes_tmp$belong_cat<- as.numeric(egoattributes_tmp$belong_cat)
describe(as.factor(egoattributes_tmp$belong_cat))
describe(egoattributes_tmp$mean.bet)


cor.test(egoattributes_tmp$mean.bet, egoattributes_tmp$belong_cat) #sig
t.test(egoattributes_tmp$mean.bet~egoattributes_tmp$belong_cat, var.equal=FALSE)
cor.test(egoattributes_tmp$density, egoattributes_tmp$belong_cat)
cor.test(egoattributes_tmp$dens, egoattributes_tmp$belong_cat)
cor.test(egoattributes_tmp$mean.deg, egoattributes_tmp$belong_cat)
cor.test(egoattributes_tmp$deg.centr, egoattributes_tmp$belong_cat)


highbelong<-subset(egoattributes_tmp, belong_cat=="high")
lowbelong<-subset(egoattributes_tmp, belong_cat=="low")

```

### Saving the final egoattribute data with network indices and all variables manipulations

```{r}
#write.csv(alterattr_tmp,"working_data/alterattr.csv")
#write.csv(egoattributes_tmp,"working_data/egoattr.csv")
#write.csv(alter_tiestmp3,"working_data/altertie.csv")
```


As of 2025, a total of `r originaln` students signed up for the study and clicked the survey. Among them, `r incompleten` consented and participated in the study. One participant was excluded due to putting in random letters. Participants who spent less than 5 minutes on the survey were also excluded (n = `r randomn-shortn`), resulting in `r shortn` participants. Next, participants who did not list a valid alter (i.e., naming self or non-person) were further excluded (n = `r shortn-namen`). Finally, participants who did not provide any alter-alter ties were excluded (n = `r finaln`), resulting in `r namen-finaln` participants.